Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2019-06-16 thirdPaper/draft/typeConeAssociahedra.tex
minor changes + biblio
minor changes

\smallskip
\begin{itemize}
\item The facet-defining inequalities of the type cone of~$\Fan$ correspond to very specific pairs of adjacent maximal cones of~$\Fan$ whose corresponding linear dependences minimally generate all such dependences. While they correspond to mesh mutations for cluster algebras and $2$-acyclic gentle brick algebras, they are not understood in general (see for instance \cref{fig:labelFacetDefiningInequalititiesNKC}\,(right)). It would be particularly interesting to fully understand these specific mutations for arbitrary (non-kissing finite) gentle algebras.

@@

@@

\begin{definition}
\label{defn::mutation conflation}
A conflation $X\infl E\defl Y$ of~$K^{[-1,0]}(\proj \Lambda)$ is called a \defn{mutation conflation} if there are basic, two-term, silting objects $X\oplus R$, $Y\oplus R$, with~$X$ and~$Y$ indecomposable, such that the inflation $X\infl E$ is a left ($\add R$)-approximation (i.e. any morphism from~$X$ to an object in~$\add R$ factors through~$X\infl E$).
\end{definition}
\begin{remark}
In \cref{defn::mutation conflation}, the requirement that~$X$ and~$Y$ are indecomposable implies the map~$E\defl Y$ is a right~($\add R$)-approximation, and that both approximations are minimal.
\end{remark}

\begin{proposition}
\label{prop::exchange conflations are unique}
Let~$\Lambda$ be a finite-dimensional~$\field$-algebra, where~$\field$ is a field. Let~$X$ and~$Y$ be objects of~$K^{[-1,0]}(\proj \Lambda)$. 
\begin{enumerate}
\item If there is a mutation conflation (see \cref{defn::mutation conflation}) of the form~$X\infl E\defl Y$, then there can be no mutation conflation of the form~$Y\infl E'\defl X$.

\item Assume that~$X\infl E\defl Y$ and~$X\infl E'\defl Y$ are two mutation conflations. 
Then~$E$ and~$E'$ are isomorphic. 
\end{enumerate} 
\end{proposition}

@@

\begin{corollary}\label{coro::silting simplicial}
 Let~$\Lambda$ be a finite dimensional brick algebra of finite representation type.
 Assume moreover that, for any indecomposable~$\Lambda$-module~$M$, the space~$\Hom{\Lambda}(M, \tau^2 M)$ vanishes.
 Then the support~$\tau$-tilting fan of~$\Lambda$ has the unique exchange property and its type cone is simplicial.
\end{corollary}

@@

\begin{corollary}\label{coro::simplicialTypeConeNKCalgebraic}
 For any~$2$-acyclic gentle brick algebra, the type cone of its support~$\tau$-tilting fan is simplicial.
\end{corollary}

@@

\begin{lemma}\label{lemma::characterization Gentle 2-acyclic}
 Let~$\Lambda$ be a~$2$-acyclic gentle brick algebra.
 Then, for any indecomposable~$\Lambda$-module~$M$ we have~$\Hom{\Lambda}(M,\tau^2 M)=0$.
\end{lemma}

>>>>

\smallskip
\begin{itemize}
\item The facet-defining inequalities of the type cone of~$\Fan$ correspond to very specific pairs of adjacent maximal cones of~$\Fan$ whose corresponding linear dependences minimally generate all such dependences. While they correspond to mesh mutations for cluster algebras and brick and $2$-acyclic gentle algebras, they are not understood in general (see for instance \cref{fig:labelFacetDefiningInequalititiesNKC}\,(right)). It would be particularly interesting to fully understand these specific mutations for arbitrary (non-kissing finite) gentle algebras.

@@

\vincent{Connect as well to Yann}

@@

\begin{definition}
\label{defn::mutation conflation}
A conflation $X\infl E\defl Y$ of~$K^{[-1,0]}(\proj \Lambda)$ is called a \defn{mutation conflation} if there are basic, two-term, silting objects $X\oplus R$, $Y\oplus R$, with~$X$ and~$Y$ indecomposable, such that the inflation $X\infl E$ is a left ($\add R$)-approximation (i.e. any morphism from~$X$ to an object in~$\add R$ factors through~$X\infl E$).
\end{definition}

\begin{remark}
In \cref{defn::mutation conflation}, the requirement that~$X$ and~$Y$ are indecomposable implies the map~$E\defl Y$ is a right~($\add R$)-approximation, and that both approximations are minimal.
\end{remark}

\begin{proposition}
\label{prop::exchange conflations are unique}
Let~$\Lambda$ be a finite-dimensional~$\field$-algebra, where~$\field$ is a field. Let~$X$ and~$Y$ be objects of~$K^{[-1,0]}(\proj \Lambda)$. 
\begin{enumerate}
\item If there is a mutation conflation (see \cref{defn::mutation conflation}) of the form~$X\infl E\defl Y$, then there can be no mutation conflation of the form~$Y\infl E'\defl X$.
\item Assume that~$X\infl E\defl Y$ and~$X\infl E'\defl Y$ are two mutation conflations. 
Then~$E$ and~$E'$ are isomorphic. 
\end{enumerate} 
\end{proposition}

@@

\begin{corollary}
\label{coro::silting simplicial}
Let~$\Lambda$ be a finite dimensional brick algebra of finite representation type.
Assume moreover that, for any indecomposable~$\Lambda$-module~$M$, the space~$\Hom{\Lambda}(M, \tau^2 M)$ vanishes.
Then the support~$\tau$-tilting fan of~$\Lambda$ has the unique exchange property and its type cone is simplicial.
\end{corollary}

@@

\begin{corollary}[\cref{coro:simplicialTypeConeNKC}]
\label{coro::simplicialTypeConeNKCalgebraic}
For any brick and $2$-acyclic gentle algebra, the type cone of its support~$\tau$-tilting fan is simplicial.
\end{corollary}

@@

\begin{lemma}
\label{lemma::characterization Gentle 2-acyclic}
Let~$\Lambda$ be a brick and $2$-acyclic gentle algebra.
Then, for any indecomposable~$\Lambda$-module~$M$ we have~$\Hom{\Lambda}(M,\tau^2 M)=0$.
\end{lemma}
